\documentclass[letter]{res}

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=17mm,
 bottom=17mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}


\begin{document}

\name{Siddhanth Sharma\\[16pt]}
\address{ (951) 318-2818 \\}
\address{
  \texttt{sshar032@ucr.edu}\\ } 
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{.05pt}}

\section{Education}
{\sl Bachelors of Science} - Computer Science (3.46/4.0)\hfill Expected: June 2020\\
University of California, Riverside \\
Centennial High School, Corona, CA
  \vspace{-2mm}
\section{Relevant Coursework}
  {\sl Computer Science}: Intro to Computer Science, Intro to Data Structures and Algorithms, \\
  C++, AP Java Programming.\\

\section{Experience}
University of California, Riverside | Riverside, CA \newline
 - {\sl Sponsorship and Operations: CitrusHack} \hfill January 2017 – Present\\
 \vspace{-2mm}
 \begin{itemize}
 \item Contacting and communicating with potential sponsors.
 \item Managing funds and planning activities and locations for the hackathon.
 \item Communication between organizing teams to balance funds and restrictions with planned activites.
 \end{itemize}
   \vspace{-2mm}

University of California, Riverside | Riverside, CA \newline - {\sl CitrusHack Participant} \hfill October 2016\\
  \vspace{-2mm}
  \begin{itemize}
  \item Created a demo for a functional mobile voting application.
  \item Worked with Android Studio, Java, XML, and FireBase.
  \end{itemize}
    \vspace{-2mm}

 Centennial High School | Corona, CA \newline - {\sl President of Husky Esports}\hfill  June 2015 – June2016\\
  \vspace{-2mm}
 \begin{itemize}
 \item Successfully created a professional gaming and programming club on campus.
 \item Allowed for pursuit of high-level competition and collaborative development in a supportive environment.
 \item Reached a total of 84 members.
 \end{itemize}
  \vspace{-2mm}
  
\section{Skills}
{\sl Programming Languages:}  C++, Java, XML \\
{\sl Operating Systems:} Linux, Windows \\ 
{\sl Software:} Android Studio, \LaTeX \\ 
 \vspace{-2mm}

\section{Projects}
CitrusPolls \newline - {\sl Group Project} \\
\begin{itemize}
  \vspace{-2mm}
  \item First Hackathon: CitrusHack 2016.
  \item Used Android Studio to create a prototype mobile voting application.
  \item Backend data transfer through FireBase.
\end{itemize}

Audio Looping Application \newline - {\sl Individual}
\begin{itemize}
  \vspace{2mm}
  \item Second Hackathon: SB Hacks 2017
  \item Used Android Studio to create a prototype live audio loop and playback application 
  \item Created for personal use as a professional beatboxer
\end{itemize}
  

\section{Activities} 
 Association of Computing Machinery (ACM) | Member (Present) \\
 Institute of Electrical and Electronics Engineers (IEEE) | Member (Present) \\

\end{resume}
\end{document}
